The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-09 article.tex
Almost there...

The quality of the JavaDocs was originally tested with DocCheck, and
later replaced by a custom written tool called OpenJavaDocCheck. With the move
to Maven (explained elsewhere) which does not have integration for this tool,
we adopted CheckStyle (\url{http://checkstyle.sourceforge.net/}). This tool
reports on missing documentation and on documentation which is not properly
annotated in the Java source files.

@@

Years of development of the CDK library has resulted in a large suite of
tests of various kinds. This include unit tests, which test core APIs, and
functional testing, which test higher level functionality of the CDK. The
latter include tests if algorithm implementations calculate the expected
values, but also contain integrated tests, which involve more than one
algorithms, such as SMILES parsing.

@@

The project continues to use PMD (\url{http://pmd.sf.net/}) for code quality checking,
but deviates from the default rules. For example, we are more liberal with 
variable name length. Moreover, a number of additional PMD tests have been
developed specifically for the CDK, that, for example, test if a class uses
the core interfaces instead of implementations of those interfaces. For example,
that the code uses IAtom instead of Atom. That said, these tests do generate a
few false positives, as the tests check the class name only, and not the
Java package the class is in.

@@

OSGi bundles are available for the CDK too, which are used by e.g. Bioclipse~\cite{spjuth2007bioclipse,spjuth2009bioclipse} and KNIME~\cite{Beisken2013}. Due to split packages between CDK modules, CDK is bundled as a single OSGi jar, which is available from \url{http://pele.farmbio.uu.se/bioclipse/cdk/cdk-1.5.13/}. This constitutes an area where improvements can be done on modularization.

>>>>

The quality of the JavaDocs was originally tested with DocCheck, and
later replaced by a custom written tool called OpenJavaDocCheck. With the move
to Maven (explained later), which does not have integration for this tool,
we adopted CheckStyle (\url{http://checkstyle.sourceforge.net/}). This tool
reports on missing documentation and on documentation which is not properly
annotated in the Java source files.

@@

Years of development of the CDK library has resulted in a large suite of
tests of various kinds. This include unit tests, which test core APIs, and
functional testing, which test higher level functionality of the CDK. The
latter include tests if algorithm implementations calculate the expected
values, but also contain integrated tests, which involve more than one
algorithm, such as SMILES parsing. The suite consists of more than 23 thousand
tests.

@@

The project continues to use PMD (\url{http://pmd.sf.net/}) for code quality checking,
but deviates from the default rules. For example, we are more liberal with 
variable name length. Moreover, a number of additional PMD tests have been
developed specifically for the CDK, that, for example, test if a class uses
the core interfaces instead of implementations of those interfaces. That is,
that the code uses \texttt{IAtom} instead of \texttt{Atom}. However, these tests do generate a
few false positives, as the tests check the class name only, and not the
Java package the class is in.

@@

OSGi bundles are available for the CDK too, which are used by e.g.
Bioclipse~\cite{spjuth2007bioclipse,spjuth2009bioclipse} and
KNIME~\cite{Beisken2013}. However, because CDK Java packages are occassionally
split between CDK modules, the CDK currently needs to be bundled as a single
OSGi jar. The bundle is available from \url{http://pele.farmbio.uu.se/bioclipse/cdk/cdk-1.5.13/}.
This Java package and bundle incompatibilities are currently being explored and
constitutes an area where improvements can be done on modularization.
